Domain Specific Languages and Code Synthesis using Haskell

### 2014-04-07 paper.tex
Fixing typo that wc used
Fixing typo with cite

It is possible to give specific types extra powers, like equality and comparison,
using the class based overloading system. In the case of \verb|Maybe|, we
can give the \verb|Maybe| type the ability to test for equality, using an
instance.
\begin{Code}
instance Eq a => Eq (Maybe a) where        
  Just a  == Just b  = a == b
  Nothing == Nothing = True
  X       == X       = False
\end{Code}

@@

Deep DSLs is a value-level way of extracting an expression, but there are ways of
extracting expressions.
Quasi-quoting is another mechanism for extracting expressions, but at the syntactic level. 
Haskell comes with an extensive template system, called Template Haskell\~cite{Sheard:02:metahaskell}, 
that is often used for DSLs. There is a sense of unease with such solutions, however, much
in the same way the C pre-processor is used, but not considered elegant. The principal issue
is that the syntax of Haskell is huge, perhaps 100 syntactical terms. An expression-based
solution, such as a deep embedding, can avoid the need to re-write front translations.
Quasi-quoting has one important advantage, specifically it can cope with control flow,
and deconstruction of values. So perhaps the future of deep DSLs is some hybrid between
expression generation and quasi-quoting, combining the best of both systems.

>>>>

It is possible to give specific types extra powers, like equality and comparison,
using the class based overloading system. In the case of \verb|Maybe|, we
can give the \verb|Maybe| type the ability to test for equality, using an
instance.
\begin{Code}
instance Eq a => Eq (Maybe a) where        
  Just a  == Just b  = a == b
  Nothing == Nothing = True
  _       == _       = False
\end{Code}

@@

Deep DSLs is a value-level way of extracting an expression, but there are ways of
extracting expressions.
Quasi-quoting is another mechanism for extracting expressions, but at the syntactic level. 
Haskell comes with an extensive template system, called Template Haskell~\cite{Sheard:02:metahaskell}, 
that is often used for DSLs. There is a sense of unease with such solutions, however, much
in the same way the C pre-processor is used, but not considered elegant. The principal issue
is that the syntax of Haskell is huge, perhaps 100 syntactical terms. An expression-based
solution, such as a deep embedding, can avoid the need to re-write front translations.
Quasi-quoting has one important advantage, specifically it can cope with control flow,
and deconstruction of values. So perhaps the future of deep DSLs is some hybrid between
expression generation and quasi-quoting, combining the best of both systems.
